---
title: "Tissue attached algae number calculation"
output: html_notebook
---

# Import library
```{r, message = FALSE}
library("EBImage")
library("ggpubr")
```

# function to calculate the cell number
input folder: folder containing inividual section image file. The folder contains the information for teatment, eg. CK, LePin_RNAi1 
file: The individual image file generated from Nikon ECLIPSE Ti2 inverted microscope. The file name contains the information of animal number, section number and categroy, eg.1-1 sample1 stalk_mouth.tif
```{r}

calculate_cell_number <- function(file,input_folder)
{
    output_folder <- paste0(input_folder,"processed_threahold0.01/")
    dir.create(output_folder)
# Get information for each image
    treatment=sub("(.*)/", "\\1", input_folder,perl=TRUE)
    sample=sub(".*(sample\\d).*", "\\1", file,perl=TRUE)
    tissue=sub(".* (.*)\\.tif","\\1",file,perl=TRUE)
# Reading image
    c2 <- readImage(paste0(input_folder,file))
# Extract alga signal from the 3rd channel
    sym <- c2[,,2]
    sym.blur <- gblur(sym, sigma = 4)
    disc = makeBrush(50, "disc")
    disc = disc / sum(disc)
# May need to adjust different offset to different batches. The purpose is to get accuate counting of alga number
    offset = 0.0007
    nuc_bg = filter2(sym.blur, disc )
    nuc_th = sym.blur > nuc_bg + offset
    nuc_th = opening(nuc_th)
    nmask = watershed(distmap(nuc_th),0.1 )
# Check how good the algae recognization it is. May need to optimize the offset if the counting is not great
    writeImage(combine(nuc_th,normalize(sym)*6), paste0(output_folder,file,"sym.jpeg"), quality = 85)
# Get the alga number
    sym_number <- max(bwlabel(nmask))
# Generate index for each alga
    nuc_th <- dilate(nuc_th,makeBrush(10,"disc"))
    symNo<- bwlabel(watershed(distmap(nuc_th),0.1 ))
# Generating tissue mask with DAPI channel signal.
    nucleus<- c2[,,1]
# Play with the threshold to fit with different batches. eg, nucleus_open <- opening(nucleus>0.02). The lower threshold will cover more region. 
    nucleus_open <- opening(nucleus>0.02)
    nucleus_mask <- opening(nucleus_open,kern = brush)
# Characterize the alga. The alga is counted as tissue attached if more than 2% and less than 90% of the algae is covered by the tissue mask
    free_sym <- function(x)
    {
        data.frame(size=sum(symNo==x), number=x, free_ratio=1-sum(nucleus_mask[symNo==x])/sum(symNo==x))
    }
    sym_charac <- sapply(1:max(symNo),free_sym)
    sym_charac <- as.data.frame(t(sym_charac))
    write.table(do.call(cbind,sym_charac),paste0(output_folder,file,"sym_statisctic.xls"),sep="\t",quote=F)
    partial_overlap_sym <- sum(sym_charac$free_ratio<0.9 & sym_charac$free_ratio >0.02)/sym_number
    free_sym <- sum(sym_charac$free_ratio>0.9)/sym_number
    writeImage(rgbImage(green=nucleus_mask, blue=nuc_th,red=nuc_th>nucleus_mask), paste0(output_folder,file,"sym_overlap.jpeg"), quality = 85)
# Calculate the cell number based on DAPI signal
    nucleus.blur <- gblur(nucleus, sigma = 0.3)
    nucleusThresh = thresh(nucleus.blur, w = 5, h = 5, offset = 0.01)
    nmask = watershed(distmap(nucleusThresh), 0.1 )
    nucleusNo <- max(bwlabel(nmask))
    writeImage(combine(nmask,normalize(nucleus)),paste0(output_folder,file,"nucleus.jpeg"), quality = 85)
    data.frame(treatment=treatment,sample=sample,symNo=sym_number,nucleusNo=nucleusNo,free_sym=free_sym,partial_sym=partial_overlap_sym,tissue=tissue,file=file)
}
```

```{r, warning = FALSE, message = FALSE }
cell_count <-list()
folders <-list.dirs()
folders <- folders[grep("/.*/",folders)]
folders <- folders[-grep("/.*/.*/",folders)]
folders <- folders[-c(13,14)]
folders <- paste0(folders,"/")
folders

brush <- makeBrush(45,"disc")
for (folder in folders){
files<- list.files(folder,pattern = "tif")
#calculate_cell_number(files[1],"CK/")
if(length(files)>0 ){
cell_count[[folder]] <-  sapply(files,calculate_cell_number,input_folder=folder)
}
}
saveRDS(cell_count,"regeneration_9d.RDS")

cell_count <- lapply(cell_count,t)
cell_count <- lapply(cell_count, as.data.frame)
cell_count <- do.call(rbind,cell_count)
temp <- rownames(cell_count)
cell_count$symNo <- as.numeric(cell_count$symNo)
cell_count$nucleusNo <- as.numeric(cell_count$nucleusNo)
cell_count$treatment <- sub(".*/(.*)/.*", "\\1", temp,perl=TRUE)
cell_count$batch <- sub("(.*)/.*/.*", "\\1", temp,perl=TRUE)
cell_count$sample <- sub(".*(sample\\d+).*", "\\1", temp,perl=TRUE)
cell_count$tissue <- sub(".* (.*).tif","\\1",temp, perl=T)
cell_count$file <- temp
cell_count$partial_sym <- as.numeric(cell_count$partial_sym)
cell_count$free_sym <-as.numeric(cell_count$free_sym)
cell_count$tissue[cell_count$tissue == "stalk_mounth"] <- "stalk_mouth"
cell_count$tissue[cell_count$tissue == "tentacel"] <- "tentacle"
cell_count$tissue<- factor(cell_count$tissue,levels = c("tentacle","tentacle_mouth","stalk_mouth","stalk"))
cell_count <- cell_count[!is.na(cell_count$tissue),]
cell_count %>% mutate(sym_percentage =symNo*(1-partial_sym-free_sym)/nucleusNo) -> cell_count
# Since the images are token by Nikon auto-foucus function. The focus of some image maybe bad if some weired strong signal appeared on the section. Need to remove these images based on eye inspection.
badsamples <- c("./20210408/CK/.9-1 sample1 stalk_mouth.tif","./20210408/LePin2/.01-1 sample1 stalk_mouth.tif",
                "./20210225/CK/.1-1 sample1 stalk_mouth.tif", "./20210225/LePin1/.9-1 sample2 stalk_mouth.tif",
                "./20210225/LePin2/.6-1 sample3 stalk_mouth.tif","./20210130/CK/.9-1 sample3 stalk_mouth.tif",
                "./20210130/CK/.4-1 sample2 stalk_mouth.tif", "./20210130/LePin1/.6-1 stalk_mouth.tif",
                "./20210130/LePin2/.7-1 sample2 stalk_mouth.tif","./20200724/CK/.6-1 sample4 stalk_mouth.tif",
                "./20210225/CK/.1-1 sample2 stalk_mouth.tif","./20210130/CK/.7-2 sample3 stalk_mouth.tif",
               "./20210130/CK/.9-1 sample1 stalk_mouth.tif","./20210408/LePin1/.9-1 sample4 stalk_mouth.tif")

cell_count <- cell_count[!rownames(cell_count) %in% badsamples,]

cell_count$treatment[cell_count$treatment=="CK"] <- "Control"
cell_count$treatment[cell_count$treatment=="LePin1"] <- "LePin shRNA -1"
cell_count$treatment[cell_count$treatment=="LePin2"] <- "LePin shRNA -2"


my_comparisons <- list( c("LePin shRNA -1", "Control"), c("LePin shRNA -2", "Control"))
p1 <- ggboxplot(cell_count, x = "treatment", y = "partial_sym",fill = "treatment",
          palette = "jco",
          add = "jitter",
          facet.by = "tissue", ncol =4,short.panel.labs = FALSE) +
    stat_compare_means(comparisons = my_comparisons,method="t.test",mapping=aes(label=..p..)) +scale_y_continuous(limits = c(0,0.53))+ rremove("xlab") + rremove("legend") +scale_x_discrete(labels=c("Control","LePin -1","LePin -2"))+
          ylab("Partial enclosed algae percentage\n (Among all algae)")                                       #    stat_compare_means(label.y.npc =  0.8)
ggpar(p1) +facet_grid( ~tissue,labeller = labeller( c("tentacle","tentacle_mouth","stalk_mouth","stalk")))
```

# Software versions
This document was computed on `r format( Sys.time(), "%a %b %d %X %Y" )` with the following R package versions.
```{r session_summary, echo=FALSE, include=TRUE, comment=NA}
    sessionInfo()
```
